paper1_results_figs_slimmed

### 2016-03-02 paper1_results_figs_slimmed.Rmd
add an edited main figs doc

---
  title: "paper1_results_figs"
  output: pdf_document
  author: "Andy South"
  date: "`r Sys.Date()`"
---

# Figures for paper 1 
# version 5 - in progress

## Based on 10000 runs with all inputs varying at once which explains the variability at particular input values.

Comparing these insecticide use strategies:

1. Single use
1. Mixture (either AI) : threshold reached for either insecticide
1. Adaptive mixture : threshold reached for either insecticide, switch to sole use of other until it too reaches threshold
1. Mixture (both AIs) : threshold reached for both insecticides in mixture
1. Sequential : sole use of one insecticide, switch to other when threshold reached until it too reaches threshold

Renamed from previous naming system :
Mixture (either AI)   [mixture1]
Mixture (both AIs)    [mixture3]
Adaptive mixture      [mixture2]

@@

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and effectiveness seem to be the most important inputs.
1. Exposure has the greatest effect on time-to-resistance.
1. Effectiveness of the insecticides is the one input that has a notably different effect on the strategies of a) sequential and b) adaptive mixture switching to sole use. Below an effectiveness of ~0.55 to 0.6 sequential takes longer, and above this 'mixture switching to sole use' takes longer.

@@

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE}

@@

## Fig. x2 How time-to-resistance is effected by input values for each insecticide use strategy

```{r, eval=TRUE, echo=FALSE, fig.height=3.5}

  names_inputs <- names(ggInsOuts)[1:num_inputs]

  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]

  for(i in names_inputs)
  {
    #x11()

    y <- 'time_to_resistance0.25'

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
            #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #tryting to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')

           )
  }

## How difference in time-to-resistance between sequential and adaptive mixture is effected by input values

```{r, eval=TRUE, echo=FALSE, fig.height=3.5}

  ggSubset <- df_diff

  names_inputs <- names(ggSubset)[1:num_inputs]

  for(i in names_inputs)
  {
    #x11()

    y <- "mixA_minus_seq0.25"

    print( ggplot(ggSubset, aes_string(x=i, y=y)) + #, colour="strategy")) + 
            #points not wanted if 10000
             geom_point(shape=1, colour="darkblue", alpha=0.2, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1, colour="red") +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i) +
             geom_hline(yintercept = 0, colour="white")
           )
  }

# Some examples showing how changing effectiveness can alter the ranking of insecticide strategies
### Curtis' Fig 2. inputs : mix2 > adaptive > mix1 > seq
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

### decrease effectiveness of I2 from 1 to 0.85 : mix2 > adaptive > seq > mix1
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

### also decrease effectiveness of I1 from 0.73 to 0.63 : seq > mix2 > adaptive > mix1
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.63 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

# PRCC difference in time-to-resistance between sequential and mixture adaptive
```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=3.5}

    x <- df_diff[,1:num_inputs]
    y <- df_diff["mixA_minus_seq0.25"]

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             ggtitle(paste("PRCC difference between sequential and mixture adaptive")) +
             xlab(NULL)
          )

# PRCC analysis for time-to-resistance subsetted by each insecticide use strategy
```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=3.5}

@@

  for(strategy in strategies)
  {

@@

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             ggtitle(paste(strategy,"PRCC")) +
             xlab(NULL)
          )
  }

@@

## response of resistance thresholds to individual inputs faceted by strategy
```{r, eval=TRUE, echo=FALSE, fig.height=3.5}

  names_inputs <- names(ggInsOuts)[1:num_inputs]

  #todo find out to take sample this doesn't work
  #ggSample <- sample(ggInsOuts,500)

  for(i in names_inputs)
  {
    #x11()

    y <- 'time_to_resistance0.25'    
    #y <- 'time_to_resistance0.5'
    color <- 'strategy'
    #coloring by exposure shows its effect even when other params are varying
    #color <- 'exposure'

    print( ggplot(ggInsOuts, aes_string(x=i, y=y, color=color)) + 
             #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             geom_smooth(colour='red', linetype='dashed',size=0.5, show.legend=FALSE) +
             facet_wrap( ~ strategy) + #, show_guide = FALSE) + 
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i))
  }

>>>>

---
title: "paper1_results_figs_slimmed"
output: pdf_document
#output: word_document
author: "Andy South"
date: "`r Sys.Date()`"
---

## Main Figures for paper 1 : version 1 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed.Rmd

@@

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture, switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and dominance have the greatest on time-to-resistance as shown in PRCC analyses.
1. Exposure has the greatest effect on time-to-resistance.
1. Effectiveness of the insecticides is the one input that has a notably different effect on the strategies of a) sequential and b) adaptive mixture switching to sole use. Below an effectiveness of ~0.55 to 0.6 sequential takes longer tp reach the resistance threshold, and above this 'mixture switching to sole use' takes longer.

@@

\pagebreak

@@

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture, switching to sole use. The latter takes slightly longer to reach the threshold.

```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=4.5}

@@

\pagebreak

# Fig x2 PRCC analysis for time-to-resistance for sequential and mixture strategies

1. Exposure and dominance have the greatest on time-to-resistance as shown in PRCC analyses.

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8}

@@

  #in main paper I want to just display sequential and mixture strategies
  strategies <- strategies[-1:-2]

  plotlist <- list(length(strategies))

  for(strategy_num in 1:length(strategies))
  {  
    strategy <- strategies[strategy_num]

@@

    #just labelling axis for final plot
    if (strategy_num == length(strategies))
    {
      axis_text_x <- element_text(angle = 45,hjust = 1, vjust = 1)
      height <- 0.9
    } else
    {
      axis_text_x <- element_blank() 
      height = 0.5
    }

    library(cowplot) # to enable setting relative heights of plots

    #draw_plot(p,x=0,y=0,width=.5,height = .5)

    # print( ggdraw() + #panel_border(remove = TRUE) +
    #          draw_plot( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
    # #print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
    #          geom_point(shape=1, colour='red') +
    #          theme(axis.text.x = axis_text_x) +
    #          #theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
    #          geom_hline(yintercept = 0, linetype=3) +
    #          ylim(-1,1) +
    #          #ggtitle(paste(strategy,"PRCC")) +
    #          ggtitle(paste(strategy,"time-to-resistance 0.25")) +
    #          xlab(NULL)
    #       , height= height))

    plotlist[[strategy_num]] <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             ggtitle(paste(strategy,"time-to-resistance 0.25")) +
             xlab(NULL) 
  }

    plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],plotlist[[4]],ncol=1, rel_heights=c(1,1,1,1.8))

@@
